---
title: ""
always_allow_html: yes
output:
  rmarkdown::html_document:
        toc: false
        toc_depth: 2
        number_sections: false
        theme: readable
        highlight: default
        toc_float: false
        code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(results="asis")
knitr::opts_chunk$set(cache=FALSE)
knitr::opts_chunk$set(echo=FALSE)
knitr::opts_chunk$set(warning=FALSE)
knitr::opts_chunk$set(message=FALSE)
knitr::opts_chunk$set(fig_cap="yes")
```

```{r, eval=FALSE, echo=FALSE}
cd ~/Sites/XGR/PiER-site
################################################
R
library(tidyverse)
## rmarkdown::render + bookdown::html_document2
rmarkdown::render("now.RMD_eCrosstalk.Rmd", bookdown::html_document2(number_sections=F,theme="readable", hightlight="default"), output_dir="/Users/hfang/Sites/XGR/PiER-site/app/examples")

q('no')
################################################
```


# {.tabset .tabset-fade}


## **Input into eCrosstalk**
Completed at `r format(Sys.time(), "%a %b %d %X %Y")` (`r Sys.timezone()`), with the runtime of `r ls_rmd$runtime` on the server side (not including the runtime on the client/user side).

> **An interactive table** of user-defined ranked genes, with 1st column `Genes` for gene symbols, 2nd column `Scores` for gene scores. For example, take as inputs the resulting output from `eCG2PG`.

```{r}
data_input <- ls_rmd$data_input

message(sprintf("'%d' '%s' (%s) ...", nrow(data_input), getwd(), as.character(Sys.time())), appendLF=TRUE)

data_input %>% DT::datatable(options=list(pageLength=5,searchHighlight=T,dom='Bfrtip',buttons=c('csv','copy'), dom='t',scrollX=T), style='default', caption="", rownames=FALSE, escape=F, extensions=c('Buttons'))
```


## **Output: pathway crosstalk**

> **A network visualisation** of pathway crosstalk, with genes/nodes color-coded by input gene scores.`r if(ls_rmd$combinedP<1){str_c(" The significance (p-value) of observing the identified crosstalk by chance is ",as.character(ls_rmd$combinedP),", as estimated by a degree-preserving node permutation test. ")}` Also provided is an editable PDF file for download.


```{r}
hlink_pdf <- oAuxEmbed(ls_rmd$pdf_crosstalk, link.text="Download PDF")
```
<div class="text-right">`r hlink_pdf`</div>

```{r crosstalk, fig.cap="The crosstalk between pathways. Genes/nodes are color-coded by input gene scores, while interactions/edges are defined by KEGG pathways.", fig.width=6, fig.height=6, echo=FALSE, eval=T, fig.align="center",out.width="50%"}
library(png)
library(grid)
#filename <- str_c('/Users/hfang/Sites/XGR/PiER-site/app/examples/', 'dTarget_crosstalk.png')
filename <- ls_rmd$png_crosstalk
img <- readPNG(filename)
grid.raster(img)
```

<hr>

> **An interactive table** of pathway crosstalk genes, with the column `Scores` for input gene scores. `Genes` are cross-referenced and hyperlinked to [GeneCards](https://www.genecards.org).

```{r}
#filename <- str_c('/Users/hfang/Sites/XGR/PiER-site/app/examples/', 'dTarget_crosstalk.xlsx')
filename <- ls_rmd$xlsx_crosstalk

message(sprintf("'%s' '%s' (%s) ...", filename, getwd(), as.character(Sys.time())), appendLF=TRUE)

tb <- openxlsx::read.xlsx(filename) %>% as_tibble() %>% mutate(Genes=sprintf("<a href='https://www.genecards.org/cgi-bin/carddisp.pl?gene=%s' target='%s''>%s</a>", name, name, name)) %>% transmute(Genes, Scores=signif(score,digits=4), Description=description)

tb %>% DT::datatable(options=list(pageLength=5,searchHighlight=T,dom='Bfrtip',buttons=c('csv','copy'), dom='t',scrollX=T), style='default', caption="", rownames=FALSE, escape=F, extensions=c('Buttons'))
```
